---
title: "Project proposal"
author: "Team number 5"
mainfont: Roboto
output:
  pdf_document:
    latex_engine: xelatex
fig_caption: true
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(htmltools)
library(readxl)
library(skimr)
library(stats)
```

```{r get_file_names}
folder_path <- "../data"

# Get the list of files in the folder
file_list <- list.files(path = folder_path, pattern = "\\.xlsx$", full.names = TRUE)
```

```{r make_high_schools_budget, warning=FALSE}
high_schools_budget <- read_excel(file_list[1])

names(high_schools_budget) <- c(
    "hebrew_year", "del1", "muni_name", "sid", "school_name", "del13",
    "sector", "pentile", "pentile_type", "del2", "is_new_horizon",
    "teaching_hours", "teaching_cost", "tutor_hours", "del3", "del4", "del5",
    "del6", "tuition", "del7", "del8", "del9", "del10", "students_regular",
    "students_special", "number_of_classes", "number_of_special_classes",
    "del11", "del12", "total_budget"
)

high_schools_budget <- high_schools_budget[, -grep("^del[0-9]+$", names(high_schools_budget))]

high_schools_budget <- high_schools_budget %>%
  mutate(
    year = case_when(
      hebrew_year == "תשפא" ~ 2021,
      hebrew_year == "תשף" ~ 2020,
      hebrew_year == "תשעט" ~ 2019,
      hebrew_year == "תשעח" ~ 2018,
      hebrew_year == "תשעז" ~ 2017,
      hebrew_year == "תשעו" ~ 2016,
      hebrew_year == "תשעה" ~ 2015,
      hebrew_year == "תשעד" ~ 2014,
      TRUE ~ NA_integer_
      ),
    pentile = as.integer(as.character(pentile)),
    pentile_type = case_when(
      pentile_type == "לא מחושב" ~ NA_character_,
      TRUE ~ pentile_type
    ),
    is_new_horizon = case_when(
      is_new_horizon == 1 ~ TRUE,
      TRUE ~ FALSE
    )
  )
```

```{r make_lamas_budget, warning=FALSE}
lamas_budget <- read_excel(file_list[2])

names(lamas_budget) <- c(
  "hebrew_year", "socio_economic_status", "del1", "del2", "del3",
  "teaching_hours", "teaching_cost", "tutor_hours", "staying_hours",
  "guidance_hours", "guidance_cost", "del4", "del5", "del6", "del7", "tuition",
  "del8", "perimeter_services_cost", "transportation_cost", "projects_cost",
  "purchases_cost", "del9", "maayan_hinuh_cost", "del10", "ptor_cost",
  "extras_ptor_cost", "number_of_students", "number_of_classes", "del11",
  "del12", "total_budget"
)

lamas_budget <- lamas_budget[, -grep("^del[0-9]+$", names(lamas_budget))]

lamas_budget <- lamas_budget %>%
  mutate(
    year = case_when(
      hebrew_year == "תשפא" ~ 2021,
      hebrew_year == "תשף" ~ 2020,
      hebrew_year == "תשעט" ~ 2019,
      hebrew_year == "תשעח" ~ 2018,
      hebrew_year == "תשעז" ~ 2017,
      hebrew_year == "תשעו" ~ 2016,
      hebrew_year == "תשעה" ~ 2015,
      hebrew_year == "תשעד" ~ 2014,
      TRUE ~ NA_integer_
      ),
    socio_economic_status = as.integer(as.character(socio_economic_status))
    )
```

```{r make_municipal_aklim, warning=FALSE}
municipal_aklim <- read_excel(file_list[3])

names(municipal_aklim) <- c(
  "mid", "muni_name", "del_edu_level", "hebrew_year", "respondents_teacher",
  "respondents_students", "respondents_teacher_percentage",
  "respondents_students_percentage", "del1", "del2", "del3", "del4", 
  "teacher_student_relations", "del5", "teacher_satisfaction", "del6", "del7",
  "del8", "reception_and_accompaniment", "del9", "violence", "del10",
  "interest", "del11", "teacher_development", "del12", "teaching_methods",
  "del13", "self_teach_strategies", "del14", "del15", "del16",
  "positive_feeling", "del17", "parents_involvement", "del18"
)

municipal_aklim <- municipal_aklim[, -grep("^del[0-9]+$", names(municipal_aklim))]

municipal_aklim <- municipal_aklim %>%
  filter(del_edu_level == 'חט"ע') %>%
  select(-del_edu_level) %>%
  mutate(
    year = case_when(
      hebrew_year == "תשפא" ~ 2021,
      hebrew_year == "תשף" ~ 2020,
      hebrew_year == "תשעט" ~ 2019,
      hebrew_year == "תשעח" ~ 2018,
      hebrew_year == "תשעז" ~ 2017,
      hebrew_year == "תשעו" ~ 2016,
      hebrew_year == "תשעה" ~ 2015,
      hebrew_year == "תשעד" ~ 2014,
      TRUE ~ NA_integer_
      )
  ) %>%
  mutate_all(~ ifelse(. == "-", NA, .))
```

```{r make_municipal_budget, warning=FALSE}
municipal_budget <- read_excel(file_list[4])

names(municipal_budget) <- c(
  "hebrew_year", "mid", "district", "muni_name", "socio_economic_status",
  "del1", "del2", "del3", "teaching_hours", "teching_hours_cost", "tutor_hours",
  "staying_hours", "guidance_hours", "guidance_hours_cost", "del4", "del5",
  "del6", "del7", "tuition", "del8", "perimeter_services_cost",
  "transportation_cost", "projects_cost", "purchases_cost", "del9", 
  "maayan_hinuh_cost", "del10", "ptor_cost", "extras_ptor_cost", 
  "number_of_students", "del11", "number_of_classes", "del12","del13", "del13", 
  "del15", "total_budget"
)

municipal_budget <- municipal_budget[, -grep("^del[0-9]+$", names(municipal_budget))]

municipal_budget <- municipal_budget %>%
  mutate(
    year = case_when(
      hebrew_year == "תשפא" ~ 2021,
      hebrew_year == "תשף" ~ 2020,
      hebrew_year == "תשעט" ~ 2019,
      hebrew_year == "תשעח" ~ 2018,
      hebrew_year == "תשעז" ~ 2017,
      hebrew_year == "תשעו" ~ 2016,
      hebrew_year == "תשעה" ~ 2015,
      hebrew_year == "תשעד" ~ 2014,
      TRUE ~ NA_integer_
      )
  ) %>%
  mutate_all(~ ifelse(. == "-", NA, .)) %>%
  mutate(
    across(teaching_hours:total_budget, ~ as.numeric(.x))
  )

```

```{r make_municipal_edu_image, warning=FALSE}
municipal_edu_image <- read_excel(file_list[5])

  # TODO: change to muni
names(municipal_edu_image) <- c(
  "hebrew_year", "muni_name", "mid", "socio_economic_status", "district", "del1", 
  "del2", "del3", "del4", "del5", "del6", "high_schools_students", "del7",
  "del8", "del9", "del10", "masters_or_higher_in_high_school", "hatamot_ivchun",
  "hatamot_no_ivchun", "olim", "spcecial_ed_in_reg", "del11", "del12",
  "number_of_classes", "del13", "del14", "del15", "total_teachers", "del16",
  "dropouts", "del17", "del18", "del19", "del20", "bagrut_entitlement",
  "bagrut_reg_ed", "bagrut_excel", "bagrut_reg_ed_excel", "english_4", 
  "english_4_reg_ed", "english_5", "english_5_reg_ed", "math_4", 
  "math_4_reg_ed", "math_5", "math_5_reg_ed", "del21", "del22", "del23",
  "del24", "del25", "del26", "class_size"
  )

municipal_edu_image <- municipal_edu_image[, -grep("^del[0-9]+$", names(municipal_edu_image))]

municipal_edu_image <- municipal_edu_image %>%
  mutate(
    year = case_when(
      hebrew_year == "תשפא" ~ 2021,
      hebrew_year == "תשף" ~ 2020,
      hebrew_year == "תשעט" ~ 2019,
      hebrew_year == "תשעח" ~ 2018,
      hebrew_year == "תשעז" ~ 2017,
      hebrew_year == "תשעו" ~ 2016,
      hebrew_year == "תשעה" ~ 2015,
      hebrew_year == "תשעד" ~ 2014,
      TRUE ~ NA_integer_
      ),
    socio_economic_status = as.integer(as.character(socio_economic_status))
  ) %>%
  mutate_all(~ ifelse(. == "לא רלוונטי", NA, .)) %>%
  mutate_all(~ ifelse(. == "לא מחושב", NA, .))
```

```{r make_schools_aklim, warning=FALSE}
schools_aklim <- read_excel(file_list[6])

names(schools_aklim) <- c(
  "questionaire_year", "district", "sid", "school_name", "del1",
  "del_edu_level", "muni_name", "sector", "type", "respondents_teacher",
  "respondents_students", "respondents_teacher_percentage", 
  "respondents_students_percentage", "del2", "del3", "del4", "del5",
  "teacher_student_relations", "del6", "teacher_satisfaction", "del7", "del8",
  "del9", "reception_and_accompaniment", "del10", "violence", "del11",
  "interest", "del12", "teacher_development", "del13", "teaching_methods",
  "del14", "self_teach_strategies", "del15", "del16", "del17",
  "positive_feeling", "del18", "parents_involvement", "del19", "del20", "del21"
  )

schools_aklim <- schools_aklim[, -grep("^del[0-9]+$", names(schools_aklim))]

schools_aklim <- schools_aklim %>%
  select(-del_edu_level) %>%
  mutate_all(~ ifelse(. == "-", NA, .))
```

```{r make_schools_edu_image, warning=FALSE}
schools_edu_image <- read_excel(file_list[8])
names(schools_edu_image) <- c(
  "hebrew_year", "educational_district", "sid", "mid", "muni_name", 
  "school_name", "exam_purity", "del1", "del2", "pentile_middle",
  "pentile_high", "del3", "decile_middle", "decile_high", "sector", "type",
  "from_grade", "to_grade", "school_plan", "tech", "del4", "olim",
  "is_special_ed", "school_type", "number_of_classes",
  "number_of_classes_yod_yodbet", "del5", "del6", "del7", "number_of_students",
  "number_of_students_yod_yodbet", "number_of_students_yodbet",
  "median_seniority", "total_teachers", "masters_or_higher_in_high_school",
  "hatamot_no_ivchun", "del8", "hatamot_ivchun", "del9", "special_ed", "del10",
  "del11", "dropouts", "del12", "del13", "del14", "dropouts_high_school",
  "youth_at_risk", "bagrut_school", "del15", "hila_students"
  )
schools_edu_image <- schools_edu_image[, -grep("^del[0-9\\w]+$", names(schools_edu_image))]
schools_edu_image <- schools_edu_image %>%
  mutate(
    year = case_when(
      hebrew_year == "תשפא" ~ 2021,
      hebrew_year == "תשף" ~ 2020,
      hebrew_year == "תשעט" ~ 2019,
      hebrew_year == "תשעח" ~ 2018,
      hebrew_year == "תשעז" ~ 2017,
      hebrew_year == "תשעו" ~ 2016,
      hebrew_year == "תשעה" ~ 2015,
      hebrew_year == "תשעד" ~ 2014,
      TRUE ~ NA_integer_
      )
  ) %>%
  mutate_all(~ ifelse(. == "לא רלוונטי", NA, .)) %>%
  mutate_all(~ ifelse(. == "לא מחושב", NA, .)) %>%
  mutate(
    tech = as.numeric(tech),
    olim = as.numeric(olim),
    across(number_of_classes:dropouts_high_school, ~ as.numeric(.x)),
    hila_students = as.numeric(hila_students)
  )
```

```{r make_schools_bagrut, warning=FALSE}
#add is youthat risk
schools_bagrut <- read_excel(file_list[7])

names(schools_bagrut) <- c(
  "hebrew_year", "district", "muni_id", "muni_name", "sid", "school_name",
  "exam_purity", "pentile_youth", "sector", "type", "del1", "del2", "del3", "del4",
  "number_of_students_yodbet", "bagrut", "del5", "bagrut_reg_ed", "del6",
  "bagrut_excell", "del7", "bagrut_reg_ed_excell", "del8", "english_4", "del9",
  "english_4_reg_ed", "del10", "english_5", "del11", "english_5_reg_ed",
  "del12", "math_4", "del13", "math_4_reg_ed", "del14", "math_5", "del15",
  "math_5_reg_ed", "del16"
  )

schools_bagrut <- schools_bagrut[, -grep("^del[0-9]+$", names(schools_bagrut))]

schools_bagrut <- schools_bagrut %>%
  mutate(
    year = case_when(
      hebrew_year == "תשפא" ~ 2021,
      hebrew_year == "תשף" ~ 2020,
      hebrew_year == "תשעט" ~ 2019,
      hebrew_year == "תשעח" ~ 2018,
      hebrew_year == "תשעז" ~ 2017,
      hebrew_year == "תשעו" ~ 2016,
      hebrew_year == "תשעה" ~ 2015,
      hebrew_year == "תשעד" ~ 2014,
      TRUE ~ NA_integer_
      ),
    youth_at_risk = case_when(
      pentile_youth == "נוער בסיכון" ~ TRUE,
      TRUE ~ FALSE
    )
  ) %>%
  left_join(schools_edu_image[, c("year", "sid", "pentile_high")], by = c("year", "sid")) %>%
  mutate(pentile = pentile_high) %>%
  select(-pentile_youth, -pentile_high)
  
schools_bagrut <- schools_bagrut %>%
  mutate_all(~ ifelse(. == "לא רלוונטי", NA, .)) %>%
  mutate_all(~ ifelse(. == "לא מחושב", NA, .)) %>%
  mutate(across(number_of_students_yodbet:math_5_reg_ed, ~ as.numeric(.x)))

```


## 1. Introduction

### How do different social, financial and educational elements affect the entitlement for 5 points Bagrut in mathematics in Israel?

This is an important question because it can help us to understand the factors that contribute to students' success in mathematics. This information can then be used to develop interventions that can help to improve students' mathematical achievement.

The general problem area that this analysis contributes to is the field of educational research. Educational research is the study of how students learn and how to improve educational outcomes. This research can be used to ensure that all students have the opportunity to succeed.

Although prior work on this specific research question is limited, we have found several additional research studies that provide relevant information. Firstly, we have found a report by the state comptroller from 2016 that highlights a decline in the percentage of students achieving 5 points in math Bagrut in recent years. This report also includes graphs illustrating the influence of sector and socioeconomic status on the rate of change in the entitlement for 5 points Bagrut. Moreover, The Information and Research Center of the Knesset has conducted a few researches on the subject. One of the studies, for example, examines the entitlement for 5 points Bagrut in mathematics from various perspectives. It analyzes the entitlement by socioeconomic status, nurturing index of the Ministry of Education, and geographical district. The other report focuses on the changes in the budget per student in the education system in recent years. Additionally, we have come across news articles published annually that provide information on the percentage of students achieving the 5 points math Bagrut per school in Israel.

Despite these existing sources, our research takes a unique approach by combining several sources of data on schools. This comprehensive approach allows us to use statistical methods to identify the most significant predictors that impact students' entitlement for 5 points Bagrut in mathematics. By extending the current body of theory and prior work, we aim to provide a deeper understanding of the factors that contribute to students' success in mathematics and inform evidence-based interventions in the Israeli education system.

## 2. Data Overview

The dataset contains various tables with information about high schools, municipalities, socio-economic factors, and educational measures in Israel. It includes data on school budgets, socio-economic status, teacher-student relations, bagrut results, and more. There are three entities in our dataset: Schools, Municipalities, Socio-economic group. Provided below are a list of family features appropriate for tackling the research question:
- Financial Features: These include variables related to high school budgets, such as teaching hours, teaching costs, tutor hours, tuition fees, and total budget allocations. 
- Socio-Economic Features: These encompass variables related to the socio-economic status of municipalities and districts, including socio-economic status and nurturing index (pentile). 
- Educational Features: These features capture various aspects of the educational environment. They include variables related to teacher-student relations, teacher satisfaction, violence, interest, teacher development, teaching methods.
- School-Specific Features: These include variables related to individual schools, such as school type, sector, and specific school-level characteristics. They capture the unique attributes of each school. 
By utilizing these major features/feature families, we can explore the relationships and dependencies between social, financial, and educational elements and their impact on the entitlement for 5 points Bagrut in mathematics.
All data collected is published in the Ministry of Education website: https://infocenter.education.gov.il/all/extensions/Shkifut_Reports/Shkifut_Reports.html


```{r}
# NEVO NEVO NEVO NEVO

# Perform the join operation
merged_data <- inner_join(schools_bagrut, schools_edu_image, by = c("sid", "year"))

# Remove duplicate columns and keep only one column with the original name
merged_data <- merged_data %>%
  select(-ends_with(".y")) %>%
  rename_with(~ gsub("\\.x$", "", .), ends_with(".x"))

# Add a new column of class size
merged_data$class_size <- merged_data$number_of_students_yod_yodbet / merged_data$number_of_classes_yod_yodbet

# Print the merged dataset with cleaned column names
print(merged_data)
```

```{r}
data <- merged_data

# Select the relevant features and target
features <- c('district', 'pentile', 'sector', 'type', 'school_type', 'tech', 
              'class_size', 'bagrut', 'masters_or_higher_in_high_school', 'median_seniority', 'bagrut_reg_ed', 'hatamot_ivchun', 'bagrut_excell', 
              'bagrut_reg_ed_excell')
target <- 'math_5_reg_ed'

# Filter the data and handle missing values if needed
filtered_data <- na.omit(data[, c(features, target)])

# Prepare the feature matrix
X <- filtered_data[, setdiff(features, target)]

# Split the dataset into features and target variables
y <- filtered_data[[target]]
```

```{r}
# Split the data into training and test sets
set.seed(368)  # For reproducibility
train_indices <- sample(nrow(X), 0.75 * nrow(X))  # 80% for training
train_X <- X[train_indices, ]
train_y <- y[train_indices]
test_X <- X[-train_indices, ]
test_y <- y[-train_indices]

# Fit the linear regression model on the training data
regression_model <- lm(train_y ~ ., data = train_X)
```

```{r}
# Print the coefficients (weights) and intercept
print("Intercept:")
print(regression_model$coefficients[1])
print("Coefficients:")
print(regression_model$coefficients[-1])

# Predict on the test set
predictions <- predict(regression_model, newdata = test_X)

# Calculate the adjusted R-squared
n <- length(test_y)
p <- length(regression_model$coefficients) - 1
adj_r_squared <- 1 - ((1 - summary(regression_model)$r.squared) * (n - 1) / (n - p - 1))
print("Adjusted R-squared:")
print(adj_r_squared)

# Calculate the mean squared error (MSE)
mse <- mean((predictions - test_y)^2)
print("Mean Squared Error (MSE):")
print(mse)

# Calculate the root mean squared error (RMSE)
rmse <- sqrt(mse)
print("Root Mean Squared Error (RMSE):")
print(rmse)
```

```{r}
# Diagnostic tests
# 1. Residuals vs. Fitted Values Plot
plot(regression_model$fitted.values, regression_model$residuals, xlab = "Fitted Values", ylab = "Residuals", main = "Residuals vs. Fitted Values Plot")

<<<<<<< Updated upstream
# 2. Normal Q-Q Plot of Residuals
{qqnorm(regression_model$residuals, main = "Normal Q-Q Plot of Residuals")
qqline(regression_model$residuals)}

# 3. Scale-Location Plot
sqrt_abs_residuals <- sqrt(abs(regression_model$residuals))
{plot(regression_model$fitted.values, sqrt_abs_residuals, xlab = "Fitted Values", ylab = "Square Root of Absolute Residuals", main = "Scale-Location Plot")
abline(h = mean(sqrt_abs_residuals), col = "red")}

```

=======
## Relationship between pentile, class size, district, and 5 points math bagrut
library(ggplot2)
library(dplyr)
>>>>>>> Stashed changes

# Nevo

```{r}
# Convert "mid" column to character type in municipal_aklim
municipal_aklim$mid <- as.character(municipal_aklim$mid)

# Perform the join operation
merged_data <- inner_join(schools_bagrut, schools_edu_image, by = c("sid", "year")) %>%
  inner_join(high_schools_budget, by = c("sid", "year")) %>%
  select(-ends_with(".y")) %>%
  select(-c("hebrew_year", "muni_name", "school_name", "sector")) %>%
  rename_with(~ gsub("\\.x$", "", .), ends_with(".x")) %>%
  mutate(
    class_size = number_of_students_yod_yodbet / number_of_classes_yod_yodbet,
    budget_per_student = total_budget / (students_regular + students_special)
  ) %>%
  inner_join(municipal_budget, by = c("mid", "year")) %>%
  inner_join(municipal_aklim, by = c("mid")) %>%
  mutate(
    teacher_student_relations = as.numeric(teacher_student_relations),
    parents_involvement = as.numeric(parents_involvement),
    violence = as.numeric(violence)
  )

# Print the merged dataset with cleaned column names
print(merged_data)

data <- merged_data
```

```{r}
# Select the relevant features and target
features <- c(
  'district.x',
  'pentile',
  'sector',
  'type',
  'school_type',
  'tech',
  'class_size',
  'bagrut',
  'masters_or_higher_in_high_school',
  'median_seniority',
  'bagrut_reg_ed',
  'hatamot_ivchun',
  'special_ed',
  'bagrut_excell',
  'bagrut_reg_ed_excell',
  'budget_per_student',
  'teaching_hours.y'
  )

target <- 'math_5_reg_ed'

# Filter the data and handle missing values if needed
filtered_data <- na.omit(data[, c(features, target)])

# Prepare the feature matrix
X <- filtered_data[, setdiff(features, target)]

# Split the dataset into features and target variables
y <- filtered_data[[target]]

# Split the data into training and test sets
set.seed(363)  # For reproducibility
train_indices <- sample(nrow(X), 0.7 * nrow(X))  # 80% for training
train_X <- X[train_indices, ]
train_y <- y[train_indices]
test_X <- X[-train_indices, ]
test_y <- y[-train_indices]

# Fit the linear regression model on the training data
regression_model <- lm(train_y ~ ., data = train_X)

# Print the coefficients (weights) and intercept
print("Intercept:")
print(regression_model$coefficients[1])
print("Coefficients:")
print(regression_model$coefficients[-1])

# Predict on the test set
predictions <- predict(regression_model, newdata = test_X)

# Calculate the adjusted R-squared
n <- length(test_y)
p <- length(regression_model$coefficients) - 1
adj_r_squared <- 1 - ((1 - summary(regression_model)$r.squared) * (n - 1) / (n - p - 1))
print("Adjusted R-squared:")
print(adj_r_squared)

# Calculate the mean squared error (MSE)
mse <- mean((predictions - test_y)^2)
print("Mean Squared Error (MSE):")
print(mse)

# Calculate the root mean squared error (RMSE)
rmse <- sqrt(mse)
print("Root Mean Squared Error (RMSE):")
print(rmse)

# Diagnostic tests
# 1. Residuals vs. Fitted Values Plot
plot(regression_model$fitted.values, regression_model$residuals, xlab = "Fitted Values", ylab = "Residuals", main = "Residuals vs. Fitted Values Plot")

# 2. Normal Q-Q Plot of Residuals
{qqnorm(regression_model$residuals, main = "Normal Q-Q Plot of Residuals")
qqline(regression_model$residuals)}

# 3. Scale-Location Plot
sqrt_abs_residuals <- sqrt(abs(regression_model$residuals))
{plot(regression_model$fitted.values, sqrt_abs_residuals, xlab = "Fitted Values", ylab = "Square Root of Absolute Residuals", main = "Scale-Location Plot")
abline(h = mean(sqrt_abs_residuals), col = "red")}

```
```{r}
#NEVO NEVO NEVO NEVO

## Relationship between pentile, class size and 5 points math bagrut
library(ggplot2)

# Create a scatter plot
ggplot(data, aes(x = class_size, y = math_5_reg_ed, color = pentile)) +
  geom_point() +
  labs(x = "Class Size", y = "Math 5 points Bagrut Entitlement", color = "Pentile")


```


```{r}
#NEVO NEVO NEVO NEVO

## Relationship between pentile, class size, district, and 5 points math bagrut
library(ggplot2)
library(dplyr)

# Perform the join operation
merged_data <- inner_join(schools_bagrut, schools_edu_image, by = c("sid", "year"))

# Remove duplicate columns and keep only one column with the original name
merged_data <- merged_data %>%
  select(-ends_with(".y")) %>%
  rename_with(~ gsub("\\.x$", "", .), ends_with(".x"))

# Add a new column of class size
merged_data$class_size <- merged_data$number_of_students_yod_yodbet / merged_data$number_of_classes_yod_yodbet

# Drop rows with NA values in pentile column
merged_data <- merged_data[complete.cases(merged_data$pentile), ]

filtered_data <- merged_data

filtered_data$class_size <- as.numeric(filtered_data$class_size)

# Create the class size bins
filtered_data$class_size_bin <- cut(filtered_data$class_size, breaks = c(10, 15, 20, 25, 30, 35, Inf), 
                                   labels = c("11-15", "16-20", "21-25", "26-30", "31-35", "36+"))

# Calculate the average math_5_reg_ed score for each pentile, class size bin, and district
average_scores <- filtered_data %>%
  group_by(pentile, class_size_bin, district) %>%
  summarize(average_score = mean(math_5_reg_ed))

# Plot the average math_5_reg_ed scores
ggplot(average_scores, aes(x = pentile, y = average_score, fill = class_size_bin)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), color = "black") +
  geom_vline(aes(xintercept = as.numeric(pentile) + 0.5), color = "black", linetype = "dashed", size = 0.5) +
  labs(x = "Pentile (Nurturing Index)", y = "5 Points Math Entitlement (%)", fill = "Class Size") +
  ggtitle("5 Points Math Entitlement by Pentile and Class Size") +
  theme_bw() +
  facet_wrap(~ district, ncol = 2)
```


```{r}
# Perform the join operation
merged_data <- inner_join(schools_bagrut, schools_edu_image, by = c("sid", "year"))

# Remove duplicate columns and keep only one column with the original name
merged_data <- merged_data %>%
  select(-ends_with(".y")) %>%
  rename_with(~ gsub("\\.x$", "", .), ends_with(".x"))

# Filter out rows where hatamot_sum is NA
merged_data <- merged_data[!is.na(merged_data$hatamot_ivchun), ]
merged_data <- merged_data[!is.na(merged_data$hatamot_no_ivchun), ]

# Adjust the scales of hatamot_sum and math_5_red_ed to range from 0 to 100
merged_data$hatamot_sum <- (merged_data$hatamot_ivchun + merged_data$hatamot_no_ivchun) * 100
merged_data$math_5_reg_ed <- merged_data$math_5_reg_ed / 1000

# Filter out rows where hatamot_sum is NA
merged_data <- merged_data[!is.na(merged_data$hatamot_sum), ]

view(merged_data)

# Create the bar graph
ggplot(merged_data, aes(x = cut(hatamot_sum, breaks = seq(0, 100, by = 10)), y = math_5_reg_ed)) +
  geom_bar(stat = "identity") +
  labs(x = "Academic Leniencies (With and Without Assessment) (%)",
       y = "5 Points In Math (%)") +
  scale_x_discrete(labels = c("0-10", "10-20", "20-30", "30-40", "40-50", "50-60", "60-70", "70-80", "80-90", "90-100")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
library(cowplot)
# Step 1: Perform an inner join
joined_data <- inner_join(schools_bagrut, schools_edu_image, by = c("sid", "year"))

# Remove duplicate columns and keep only one column with the original name
joined_data <- joined_data %>%
  select(-ends_with(".y")) %>%
  rename_with(~ gsub("\\.x$", "", .), ends_with(".x"))

joined_data$hatamot_sum <- (joined_data$hatamot_ivchun + joined_data$hatamot_no_ivchun)

# Create subsets based on total hatamot threshold
subset1 <- filter(joined_data, hatamot_sum >= 0.7)
subset2 <- filter(joined_data, hatamot_sum < 0.7)

# Calculate proportions for youth_at_risk and pentile within each subset
prop_youth_at_risk_subset1 <- nrow(filter(subset1, youth_at_risk)) / nrow(subset1)
prop_youth_at_risk_subset2 <- nrow(filter(subset2, youth_at_risk)) / nrow(subset2)

# Plot 1: Proportion of youth_at_risk = TRUE
plot1 <- ggplot() +
  geom_bar(data = data.frame(x = c("Leniencies >= 70%", "Leniencies < 70%"),
                             prop = c(prop_youth_at_risk_subset1, prop_youth_at_risk_subset2)),
           aes(x, prop * 100, fill = x), stat = "identity") +
  scale_fill_manual(values = c("#F8766D", "#00BFC4"), guide = FALSE) +
  labs(x = "", y = "Youth at Risk (%)", title = "Proportion of Youth at Risk") +
  scale_y_continuous(limits = c(0, 30)) +
  theme_minimal()

# Plot 2: Average special_ed
plot2 <- ggplot() +
  geom_bar(data = subset1, aes(x = "Leniencies >= 70%", y = special_ed), stat = "summary",fill = "#00BFC4") +
  geom_bar(data = subset2, aes(x = "Leniencies < 70%", y = special_ed), stat = "summary", fill = "#F8766D") +
  labs(x = "", y = "Special Education", title = "Average Special Education")
  theme_minimal()

# Combine the plots into a single graph
combined_plot <- cowplot::plot_grid(plot1, plot2, nrow = 1)

# Display the combined graph
print(combined_plot)
```


```{r}
# Filter municipalities with over 1500 high_schools_students in 2014
filtered_mid <- municipal_edu_image %>%
  filter(year == 2014, high_schools_students >= 4500) %>%
  distinct(mid)

# Filter municipal_edu_image dataset based on filtered_mid
filtered_data <- municipal_edu_image %>%
  filter(mid %in% filtered_mid$mid)

# Convert "class_size" and "math_5_reg_ed" columns to numeric
filtered_data$class_size <- as.numeric(filtered_data$class_size)
filtered_data$math_5_reg_ed <- as.numeric(filtered_data$math_5_reg_ed)

# Plot the class_size for each muni_name
ggplot(filtered_data, aes(x = year, y = class_size, color = muni_name, group = muni_name)) +
  geom_line(size = 1) +
  labs(x = "Year", y = "Class Size", color = "Municipality") +
  theme_minimal() +
  theme(legend.position = "right") +
  scale_y_continuous(limits = c(23, 30), breaks = seq(23, 30, by = 2))

# Plot the math_5_reg_ed for each muni_name
ggplot(filtered_data, aes(x = year, y = math_5_reg_ed, color = muni_name, group = muni_name)) +
  geom_line(size = 1) +
  labs(x = "Year", y = "Math 5 Reg Ed", color = "Municipality") +
  theme_minimal() +
  theme(legend.position = "right")

# Filter municipalities with over 1500 high_schools_students in 2014
filtered_mid <- municipal_edu_image %>%
  filter(year == 2014, high_schools_students >= 4500) %>%
  distinct(mid)

# Filter municipal_edu_image dataset based on filtered_mid
filtered_data <- municipal_edu_image %>%
  filter(mid %in% filtered_mid$mid)

# Convert "masters_or_higher_in_higher_school" column to numeric
filtered_data$masters_or_higher_in_high_school <- as.numeric(filtered_data$masters_or_higher_in_high_school)

# Plot the math_5_reg_ed for each muni_name
ggplot(filtered_data, aes(x = year, y = masters_or_higher_in_high_school, color = muni_name, group = muni_name)) +
  geom_line(size = 1) +
  labs(x = "Year", y = "Masters Or Higher In High School", color = "Municipality") +
  theme_minimal() +
  theme(legend.position = "right")
  scale_y_continuous(limits = c(0, 100), breaks = seq(20, 90, by = 10))
  
  # Filter municipalities with over 1500 high_schools_students in 2014
filtered_mid <- municipal_edu_image %>%
  filter(year == 2014, high_schools_students >= 4500) %>%
  distinct(mid)

# Filter municipal_edu_image dataset based on filtered_mid
filtered_data <- municipal_edu_image %>%
  filter(mid %in% filtered_mid$mid)

# Convert "hatamot_ivchun" and "hatamot_no_ivchun" columns to numeric
filtered_data$hatamot_ivchun <- as.numeric(filtered_data$hatamot_ivchun)
filtered_data$hatamot_no_ivchun <- as.numeric(filtered_data$hatamot_no_ivchun)

# Calculate the sum of hatamot_ivchun and hatamot_no_ivchun
filtered_data$sum_hatamot <- filtered_data$hatamot_ivchun + filtered_data$hatamot_no_ivchun

# Plot the sum of hatamot_ivchun and hatamot_no_ivchun for each muni_name
ggplot(filtered_data, aes(x = year, y = sum_hatamot, color = muni_name, group = muni_name)) +
  geom_line(size = 1) +
  labs(x = "Year", y = "Sum of Hatamot", color = "Municipality") +
  theme_minimal() +
  theme(legend.position = "right")

```

```{r}
## Relationship between pentile, class size, district, and 5 points math bagrut
library(ggplot2)
library(dplyr)

# Create the class size bins
filtered_data$class_size_bin <- cut(filtered_data$class_size, breaks = c(0, 5, 10, 15, 20, 25, 30, 35, Inf), 
                                   labels = c("0-5", "6-10", "11-15", "16-20", "21-25", "26-30", "31-35", "36+"))

# Calculate the average math_5_reg_ed score for each pentile, class size bin, and district
average_scores <- filtered_data %>%
  group_by(pentile, class_size_bin, district) %>%
  summarize(average_score = mean(math_5_reg_ed))

# Plot the average math_5_reg_ed scores
ggplot(average_scores, aes(x = pentile, y = average_score, fill = class_size_bin)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), color = "black") +
  geom_vline(aes(xintercept = as.numeric(pentile) + 0.5), color = "black", linetype = "dashed", size = 0.5) +
  labs(x = "Pentile", y = "Average math_5_reg_ed Score", fill = "Class Size") +
  ggtitle("Average math_5_reg_ed Score by Pentile and Class Size") +
  theme_bw() +
  facet_wrap(~ district, ncol = 2)
```


```{r}
# Perform the join operation
merged_data <- inner_join(schools_bagrut, schools_edu_image, by = c("sid", "year")) %>%
  inner_join(high_schools_budget, by = c("sid", "year")) %>%
  select(-ends_with(".y")) %>%
  select(-c("hebrew_year", "muni_name", "school_name", "sector")) %>%
  rename_with(~ gsub("\\.x$", "", .), ends_with(".x")) %>%

view(merged_data)

# Perform the join operation
merged_data <- inner_join(schools_bagrut, schools_edu_image, by = c("sid", "year")) %>%
  select(-ends_with(".y")) %>%
  rename_with(~ gsub("\\.x$", "", .), ends_with(".x"))

# Filter the joined dataset based on the given criteria
filtered_high_schools <- merged_data %>%
  filter(pentile_high == "2", sector == "יהודי", year == 2021)

# Convert "hatamot_no_ivhun" and "hatamot_ivchun" columns to numeric
filtered_high_schools$hatamot_no_ivchun <- as.numeric(filtered_high_schools$hatamot_no_ivchun)
filtered_high_schools$hatamot_ivchun <- as.numeric(filtered_high_schools$hatamot_ivchun)

# Create a scatter plot
ggplot(filtered_high_schools, aes(x = hatamot_no_ivchun + hatamot_ivchun, y = math_5_reg_ed)) +
  geom_point() +
  labs(x = "Sum of Hatamot", y = "Math 5 Reg Ed") +
  theme_minimal()
```

```{r}

```

```{r}

```

# Fabian
```{r}
# Perform the join operation
merged_data <- inner_join(schools_bagrut, schools_edu_image, by = c("sid", "year")) %>%
  inner_join(high_schools_budget, by = c("sid", "year")) %>%
  select(-ends_with(".y")) %>%
  select(-c("hebrew_year", "muni_name", "school_name", "sector")) %>%
  rename_with(~ gsub("\\.x$", "", .), ends_with(".x")) %>%
  mutate(
    class_size = number_of_students_yod_yodbet / number_of_classes_yod_yodbet,
    budget_per_student = total_budget / (students_regular + students_special)
  ) %>%
  inner_join(municipal_budget, by = c("mid", "year"))

# Print the merged dataset with cleaned column names
print(merged_data)

data <- merged_data

# Select the relevant features and target
features <- c(
  'district.x',
  'pentile',
  'sector',
  'type',
  'school_type',
  'tech',
  'class_size',
  'bagrut',
  'masters_or_higher_in_high_school',
  'median_seniority',
  'bagrut_reg_ed',
  'hatamot_ivchun',
  'special_ed',
  'bagrut_excell',
  'bagrut_reg_ed_excell',
  'budget_per_student',
  'teaching_hours.y'
  )

target <- 'math_5_reg_ed'

# Filter the data and handle missing values if needed
filtered_data <- na.omit(data[, c(features, target)])

# Prepare the feature matrix
X <- filtered_data[, setdiff(features, target)]

# Split the dataset into features and target variables
y <- filtered_data[[target]]

# Split the data into training and test sets
set.seed(368)  # For reproducibility
train_indices <- sample(nrow(X), 0.8 * nrow(X))  # 80% for training
train_X <- X[train_indices, ]
train_y <- y[train_indices]
test_X <- X[-train_indices, ]
test_y <- y[-train_indices]

# Fit the linear regression model on the training data
regression_model <- lm(train_y ~ ., data = train_X)

# Print the coefficients (weights) and intercept
print("Intercept:")
print(regression_model$coefficients[1])
print("Coefficients:")
print(regression_model$coefficients[-1])

# Predict on the test set
predictions <- predict(regression_model, newdata = test_X)

# Calculate the adjusted R-squared
n <- length(test_y)
p <- length(regression_model$coefficients) - 1
adj_r_squared <- 1 - ((1 - summary(regression_model)$r.squared) * (n - 1) / (n - p - 1))
print("Adjusted R-squared:")
print(adj_r_squared)

# Calculate the mean squared error (MSE)
mse <- mean((predictions - test_y)^2)
print("Mean Squared Error (MSE):")
print(mse)

# Calculate the root mean squared error (RMSE)
rmse <- sqrt(mse)
print("Root Mean Squared Error (RMSE):")
print(rmse)

# Diagnostic tests
# 1. Residuals vs. Fitted Values Plot
plot(regression_model$fitted.values, regression_model$residuals, xlab = "Fitted Values", ylab = "Residuals", main = "Residuals vs. Fitted Values Plot")

# 2. Normal Q-Q Plot of Residuals
{qqnorm(regression_model$residuals, main = "Normal Q-Q Plot of Residuals")
qqline(regression_model$residuals)}

# 3. Scale-Location Plot
sqrt_abs_residuals <- sqrt(abs(regression_model$residuals))
{plot(regression_model$fitted.values, sqrt_abs_residuals, xlab = "Fitted Values", ylab = "Square Root of Absolute Residuals", main = "Scale-Location Plot")
abline(h = mean(sqrt_abs_residuals), col = "red")}

```

```{r}

```

# Dvir
```{r}

```

```{r}

```

```{r}

```

