---
title: "Project proposal"
author: "Team number 5"
mainfont: Roboto
output:
  pdf_document:
    latex_engine: xelatex
fig_caption: true
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(htmltools)
library(readxl)
library(skimr)
```

```{r get_file_names}
folder_path <- "../data"

# Get the list of files in the folder
file_list <- list.files(path = folder_path, pattern = "\\.xlsx$", full.names = TRUE)
```

```{r make_high_schools_budget, warning=FALSE}
high_schools_budget <- read_excel(file_list[1])

names(high_schools_budget) <- c(
    "hebrew_year", "del1", "muni_name", "sid", "school_name", "del13",
    "sector", "pentile", "pentile_type", "del2", "is_new_horizon",
    "teaching_hours", "teaching_cost", "tutor_hours", "del3", "del4", "del5",
    "del6", "tuition", "del7", "del8", "del9", "del10", "students_regular",
    "students_special", "number_of_classes", "number_of_special_classes",
    "del11", "del12", "total_budget"
)

high_schools_budget <- high_schools_budget[, -grep("^del[0-9]+$", names(high_schools_budget))]

high_schools_budget <- high_schools_budget %>%
  mutate(
    year = case_when(
      hebrew_year == "תשפא" ~ 2021,
      hebrew_year == "תשף" ~ 2020,
      hebrew_year == "תשעט" ~ 2019,
      hebrew_year == "תשעח" ~ 2018,
      hebrew_year == "תשעז" ~ 2017,
      hebrew_year == "תשעו" ~ 2016,
      hebrew_year == "תשעה" ~ 2015,
      hebrew_year == "תשעד" ~ 2014,
      TRUE ~ NA_integer_
      ),
    pentile = as.integer(as.character(pentile)),
    pentile_type = case_when(
      pentile_type == "לא מחושב" ~ NA_character_,
      TRUE ~ pentile_type
    ),
    is_new_horizon = case_when(
      is_new_horizon == 1 ~ TRUE,
      TRUE ~ FALSE
    )
  )
```

```{r make_lamas_budget, warning=FALSE}
lamas_budget <- read_excel(file_list[2])

names(lamas_budget) <- c(
  "hebrew_year", "socio_economic_status", "del1", "del2", "del3",
  "teaching_hours", "teaching_cost", "tutor_hours", "staying_hours",
  "guidance_hours", "guidance_cost", "del4", "del5", "del6", "del7", "tuition",
  "del8", "perimeter_services_cost", "transportation_cost", "projects_cost",
  "purchases_cost", "del9", "maayan_hinuh_cost", "del10", "ptor_cost",
  "extras_ptor_cost", "number_of_students", "number_of_classes", "del11",
  "del12", "total_budget"
)

lamas_budget <- lamas_budget[, -grep("^del[0-9]+$", names(lamas_budget))]

lamas_budget <- lamas_budget %>%
  mutate(
    year = case_when(
      hebrew_year == "תשפא" ~ 2021,
      hebrew_year == "תשף" ~ 2020,
      hebrew_year == "תשעט" ~ 2019,
      hebrew_year == "תשעח" ~ 2018,
      hebrew_year == "תשעז" ~ 2017,
      hebrew_year == "תשעו" ~ 2016,
      hebrew_year == "תשעה" ~ 2015,
      hebrew_year == "תשעד" ~ 2014,
      TRUE ~ NA_integer_
      ),
    socio_economic_status = as.integer(as.character(socio_economic_status))
    )
```

```{r make_municipal_aklim, warning=FALSE}
municipal_aklim <- read_excel(file_list[3])

  # TODO: change to muni
names(municipal_aklim) <- c(
  "cid", "city", "del_edu_level", "hebrew_year", "respondents_teacher",
  "respondents_students", "respondents_teacher_percentage",
  "respondents_students_percentage", "del1", "del2", "del3", "del4", 
  "teacher_student_relations", "del5", "teacher_satisfaction", "del6", "del7",
  "del8", "reception_and_accompaniment", "del9", "violence", "del10",
  "interest", "del11", "teacher_development", "del12", "teaching_methods",
  "del13", "self_teach_strategies", "del14", "del15", "del16",
  "positive_feeling", "del17", "parents_involvement", "del18"
)

municipal_aklim <- municipal_aklim[, -grep("^del[0-9]+$", names(municipal_aklim))]

municipal_aklim <- municipal_aklim %>%
  filter(del_edu_level == 'חט"ע') %>%
  select(-del_edu_level) %>%
  mutate(
    year = case_when(
      hebrew_year == "תשפא" ~ 2021,
      hebrew_year == "תשף" ~ 2020,
      hebrew_year == "תשעט" ~ 2019,
      hebrew_year == "תשעח" ~ 2018,
      hebrew_year == "תשעז" ~ 2017,
      hebrew_year == "תשעו" ~ 2016,
      hebrew_year == "תשעה" ~ 2015,
      hebrew_year == "תשעד" ~ 2014,
      TRUE ~ NA_integer_
      )
  ) %>%
  mutate_all(~ ifelse(. == "-", NA, .))
```

```{r make_municipal_edu_image, warning=FALSE}
municipal_edu_image <- read_excel(file_list[4])

  # TODO: change to muni
names(municipal_edu_image) <- c(
  "hebrew_year", "city", "cid", "socio_economic_status", "district", "del1", 
  "del2", "del3", "del4", "del5", "del6", "high_schools_students", "del7",
  "del8", "del9", "del10", "masters_or_higher_in_high_school", "hatamot_ivchun",
  "hatamot_no_ivchun", "olim", "spcecial_ed_in_reg", "del11", "del12",
  "number_of_classes", "del13", "del14", "del15", "total_teachers", "del16",
  "dropouts", "del17", "del18", "del19", "del20", "bagrut_entitlement",
  "bagrut_reg_ed", "bagrut_excel", "bagrut_reg_ed_excel", "english_4", 
  "english_4_reg_ed", "english_5", "english_5_reg_ed", "math_4", 
  "math_4_reg_ed", "math_5", "math_5_reg_ed", "del21", "del22", "del23",
  "del24", "del25", "del26", "del27", "class_size"
  )

municipal_edu_image <- municipal_edu_image[, -grep("^del[0-9]+$", names(municipal_edu_image))]

municipal_edu_image <- municipal_edu_image %>%
  mutate(
    year = case_when(
      hebrew_year == "תשפא" ~ 2021,
      hebrew_year == "תשף" ~ 2020,
      hebrew_year == "תשעט" ~ 2019,
      hebrew_year == "תשעח" ~ 2018,
      hebrew_year == "תשעז" ~ 2017,
      hebrew_year == "תשעו" ~ 2016,
      hebrew_year == "תשעה" ~ 2015,
      hebrew_year == "תשעד" ~ 2014,
      TRUE ~ NA_integer_
      ),
    socio_economic_status = as.integer(as.character(socio_economic_status))
  ) %>%
  mutate_all(~ ifelse(. == "לא רלוונטי", NA, .)) %>%
  mutate_all(~ ifelse(. == "לא מחושב", NA, .))
```

```{r make_schools_aklim, warning=FALSE}
schools_aklim <- read_excel(file_list[5])

names(schools_aklim) <- c(
  "questionaire_year", "district", "school_id", "school_name", "del1",
  "del_edu_level", "muni_name", "sector", "type", "respondents_teacher",
  "respondents_students", "respondents_teacher_percentage", 
  "respondents_students_percentage", "del2", "del3", "del4", "del5",
  "teacher_student_relations", "del6", "teacher_satisfaction", "del7", "del8",
  "del9", "reception_and_accompaniment", "del10", "violence", "del11",
  "interest", "del12", "teacher_development", "del13", "teaching_methods",
  "del14", "self_teach_strategies", "del15", "del16", "del17",
  "positive_feeling", "del18", "parents_involvement", "del19", "del20", "del21"
  )

schools_aklim <- schools_aklim[, -grep("^del[0-9]+$", names(schools_aklim))]

schools_aklim <- schools_aklim %>%
  select(-del_edu_level) %>%
  mutate_all(~ ifelse(. == "-", NA, .))
```

```{r make_schools_edu_image, warning=FALSE}
schools_edu_image <- read_excel(file_list[7])
names(schools_edu_image) <- c(
  "hebrew_year", "educational_district", "sid", "cid", "muni_name", 
  "school_name", "exam_putiry", "del1", "del2", "pentile_middle",
  "pentile_high", "del3", "decile_middle", "decile_high", "sector", "type",
  "from_grade", "to_grade", "school_plan", "tech", "del4", "olim",
  "is_special_ed", "schooly_type", "number_of_classes",
  "number_of_classes_yod_yodbet", "del5", "del6", "del7", "number_of_students",
  "number_of_students_yod_yodbet", "number_of_students_yodbet",
  "median_seniority", "total_teachers", "masters_or_higher_in_high_school",
  "hatamot_no_ivhun", "del8", "hatamot_ivchun", "del9", "special_ed", "del10",
  "del11", "dropouts", "del12", "del13", "del14", "dropouts_high_school",
  "youth_at_risk", "bagrut_school", "del15", "hila_students"
  )
schools_edu_image <- schools_edu_image[, -grep("^del[0-9\\w]+$", names(schools_edu_image))]
schools_edu_image <- schools_edu_image %>%
  mutate(
    year = case_when(
      hebrew_year == "תשפא" ~ 2021,
      hebrew_year == "תשף" ~ 2020,
      hebrew_year == "תשעט" ~ 2019,
      hebrew_year == "תשעח" ~ 2018,
      hebrew_year == "תשעז" ~ 2017,
      hebrew_year == "תשעו" ~ 2016,
      hebrew_year == "תשעה" ~ 2015,
      hebrew_year == "תשעד" ~ 2014,
      TRUE ~ NA_integer_
      )
  ) %>%
  mutate_all(~ ifelse(. == "לא רלוונטי", NA, .)) %>%
  mutate_all(~ ifelse(. == "לא מחושב", NA, .))
```

```{r make_schools_bagrut, warning=FALSE}
#add is youthat risk
schools_bagrut <- read_excel(file_list[6])

names(schools_bagrut) <- c(
  "hebrew_year", "district", "muni_id", "muni_name", "sid", "school_name",
  "exam_putiry", "pentile_youth", "sector", "type", "del1", "del2", "del3", "del4",
  "number_of_students_yodbet", "bagrut", "del5", "bagrut_reg_ed", "del6",
  "bagrut_excell", "del7", "bagrut_reg_ed_excell", "del8", "english_4", "del9",
  "english_4_reg_ed", "del10", "english_5", "del11", "english_5_reg_ed",
  "del12", "math_4", "del13", "math_4_reg_ed", "del14", "math_5", "del15",
  "math_5_reg_ed", "del16"
  )

schools_bagrut <- schools_bagrut[, -grep("^del[0-9]+$", names(schools_bagrut))]

schools_bagrut <- schools_bagrut %>%
  mutate(
    year = case_when(
      hebrew_year == "תשפא" ~ 2021,
      hebrew_year == "תשף" ~ 2020,
      hebrew_year == "תשעט" ~ 2019,
      hebrew_year == "תשעח" ~ 2018,
      hebrew_year == "תשעז" ~ 2017,
      hebrew_year == "תשעו" ~ 2016,
      hebrew_year == "תשעה" ~ 2015,
      hebrew_year == "תשעד" ~ 2014,
      TRUE ~ NA_integer_
      ),
    youth_at_risk = case_when(
      pentile_youth == "נוער בסיכון" ~ TRUE,
      TRUE ~ FALSE
    )
  ) %>%
  left_join(schools_edu_image[, c("year", "sid", "pentile_high")], by = c("year", "sid")) %>%
  mutate(pentile = pentile_high) %>%
  select(-pentile_youth, -pentile_high)

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```


## 1. Introduction

### How do different social, financial and educational elements affect the entitlement for 5 points Bagrut in mathematics in Israel?

This is an important question because it can help us to understand the factors that contribute to students' success in mathematics. This information can then be used to develop interventions that can help to improve students' mathematical achievement.

The general problem area that this analysis contributes to is the field of educational research. Educational research is the study of how students learn and how to improve educational outcomes. This research can be used to ensure that all students have the opportunity to succeed.

Although prior work on this specific research question is limited, we have found several additional research studies that provide relevant information. Firstly, we have found a report by the state comptroller from 2016 that highlights a decline in the percentage of students achieving 5 points in math Bagrut in recent years. This report also includes graphs illustrating the influence of sector and socioeconomic status on the rate of change in the entitlement for 5 points Bagrut. Moreover, The Information and Research Center of the Knesset has conducted a few researches on the subject. One of the studies, for example, examines the entitlement for 5 points Bagrut in mathematics from various perspectives. It analyzes the entitlement by socioeconomic status, nurturing index of the Ministry of Education, and geographical district. The other report focuses on the changes in the budget per student in the education system in recent years. Additionally, we have come across news articles published annually that provide information on the percentage of students achieving the 5 points math Bagrut per school in Israel.

Despite these existing sources, our research takes a unique approach by combining several sources of data on schools. This comprehensive approach allows us to use statistical methods to identify the most significant predictors that impact students' entitlement for 5 points Bagrut in mathematics. By extending the current body of theory and prior work, we aim to provide a deeper understanding of the factors that contribute to students' success in mathematics and inform evidence-based interventions in the Israeli education system.

## 2. Data Overview

The dataset contains various tables with information about high schools, municipalities, socio-economic factors, and educational measures in Israel. It includes data on school budgets, socio-economic status, teacher-student relations, bagrut results, and more. There are three entities in our dataset: Schools, Municipalities, Socio-economic group. Provided below are a list of family features appropriate for tackling the research question:
- Financial Features: These include variables related to high school budgets, such as teaching hours, teaching costs, tutor hours, tuition fees, and total budget allocations. 
- Socio-Economic Features: These encompass variables related to the socio-economic status of municipalities and districts, including socio-economic status and nurturing index (pentile). 
- Educational Features: These features capture various aspects of the educational environment. They include variables related to teacher-student relations, teacher satisfaction, violence, interest, teacher development, teaching methods.
- School-Specific Features: These include variables related to individual schools, such as school type, sector, and specific school-level characteristics. They capture the unique attributes of each school. 
By utilizing these major features/feature families, we can explore the relationships and dependencies between social, financial, and educational elements and their impact on the entitlement for 5 points Bagrut in mathematics.
All data collected is published in the Ministry of Education website: https://infocenter.education.gov.il/all/extensions/Shkifut_Reports/Shkifut_Reports.html


```{r}

```

```{r}
# Load the required packages
library(readxl)
library(dplyr)
library(stats)

# Read the Excel file
data <- read_excel("C:/University/Sem 2 Year 2/Tichnut mitkadem/project/data/schools-bagrut.xlsx")

# Select the relevant features and target
features <- c('exam_purity', 'pentile', 'is_youth_at_risk', 'sector', 'type',
              'number_of_students_yodbet', 'bagrut', 'bagrut_reg_ed', 'bagrut_excell',
              'bagrut_reg_ed_excell')
target <- 'math_5_reg_ed'

# Filter the data and handle missing values if needed
filtered_data <- na.omit(data[, c(features, target)])

# Convert categorical variables to factors
filtered_data$exam_purity <- as.factor(filtered_data$exam_purity)
filtered_data$sector <- as.factor(filtered_data$sector)
filtered_data$type <- as.factor(filtered_data$type)

# Create dummy variables for the categorical features
dummy_vars <- model.matrix(~ exam_purity + sector + type - 1, data = filtered_data)

# Combine the dummy variables with the numerical features
X <- cbind(filtered_data[, setdiff(features, c('exam_purity', 'sector', 'type'))], dummy_vars)

# Split the dataset into features and target variables
y <- filtered_data[, target]

# Fit the linear regression model
regression_model <- lm(y ~ ., data = X)

# Print the coefficients (weights) and intercept
print("Intercept:")
print(regression_model$coefficients[1])
print("Coefficients:")
print(regression_model$coefficients[-1])

```

```{r}
# Load the required packages
library(readxl)
library(dplyr)
library(stats)

# Read the Excel files
dataset1 <- read_excel("C:/University/Sem 2 Year 2/Tichnut mitkadem/project/data/schools-bagrut.xlsx")
dataset2 <- read_excel("C:/University/Sem 2 Year 2/Tichnut mitkadem/project/data/schools-edu-image.xlsx")

# Perform the join operation
merged_data <- inner_join(dataset1, dataset2, by = c("school_id" = "sid", "year"))

# Print the merged dataset
print(merged_data)
```

```{r}
# NEVO NEVO NEVO NEVO
# Load the required packages
library(readxl)
library(dplyr)
library(stats)

# Read the Excel files
dataset1 <- read_excel("C:/Users/user/OneDrive/שולחן העבודה/Nevo/סמסטר ד/תכנות מתקדם לניתוח נתונים/פרוייקט גמר תכנות מתקדם/data/schools-bagrut.xlsx")
dataset2 <- read_excel("C:/Users/user/OneDrive/שולחן העבודה/Nevo/סמסטר ד/תכנות מתקדם לניתוח נתונים/פרוייקט גמר תכנות מתקדם/data/schools-edu-image.xlsx")

# Perform the join operation
merged_data <- inner_join(dataset1, dataset2, by = c("school_id" = "sid", "year"))

# Remove duplicate columns and keep only one column with the original name
merged_data <- merged_data %>%
  select(-ends_with(".y")) %>%
  rename_with(~ gsub("\\.x$", "", .), ends_with(".x"))

# Add a new column of class size
merged_data$class_size <- merged_data$number_of_students_yod_yodbet / merged_data$number_of_classes_yod_yodbet

# Print the merged dataset with cleaned column names
print(merged_data)
# Print the merged data, ordered by "pentile" column in ascending order
print(merged_data %>% arrange(pentile))

glimpse(merged_data)

```


```{r}
#NEVO NEVO NEVO NEVO

# Load the required packages
library(readxl)
library(dplyr)
library(stats)

# Read the Excel file
data <- merged_data

# Select the relevant features and target
features <- features <- c('district', 'pentile', 'sector', 'type', 'school_type', 'tech',
              'class_size', 'bagrut', 'masters_or_higher_in_high_school', 'median_seniority', 'bagrut_reg_ed', 'bagrut_excell',
              'bagrut_reg_ed_excell')
target <- 'math_5_reg_ed'

# Filter the data and handle missing values if needed
filtered_data <- na.omit(data[, c(features, target)])

# Prepare the feature matrix
X <- filtered_data[, setdiff(features, target)]

# Split the dataset into features and target variables
y <- filtered_data[[target]]

# Fit the linear regression model
regression_model <- lm(y ~ ., data = X)

# Print the coefficients (weights) and intercept
print("Intercept:")
print(regression_model$coefficients[1])
print("Coefficients:")
print(regression_model$coefficients[-1])
```

```{r}
#NEVO NEVO NEVO NEVO

## Relationship between pentile, class size and 5 points math bagrut
library(ggplot2)

# Create a scatter plot
ggplot(data, aes(x = class_size, y = math_5_reg_ed, color = pentile)) +
  geom_point() +
  labs(x = "Class Size", y = "Math 5 points Bagrut Entitlement", color = "Pentile")


```
```{r}
#NEVO NEVO NEVO NEVO

## Relationship between pentile, class size, district, and 5 points math bagrut
library(ggplot2)
library(dplyr)

# Create the class size bins
filtered_data$class_size_bin <- cut(filtered_data$class_size, breaks = c(0, 5, 10, 15, 20, 25, 30, 35, Inf), 
                                   labels = c("0-5", "6-10", "11-15", "16-20", "21-25", "26-30", "31-35", "36+"))

# Calculate the average math_5_reg_ed score for each pentile, class size bin, and district
average_scores <- filtered_data %>%
  filter(tech <= 50) %>%
  group_by(pentile, class_size_bin, district) %>%
  summarize(average_score = mean(math_5_reg_ed))

# Plot the average math_5_reg_ed scores
ggplot(average_scores, aes(x = pentile, y = average_score, fill = class_size_bin)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), color = "black") +
  geom_vline(aes(xintercept = as.numeric(pentile) + 0.5), color = "black", linetype = "dashed", size = 0.5) +
  labs(x = "Pentile", y = "Average math_5_reg_ed Score", fill = "Class Size") +
  ggtitle("Average math_5_reg_ed Score by Pentile and Class Size") +
  theme_bw() +
  facet_wrap(~ district, ncol = 2)
```

```{r}
# Calculate the average class size by sector
average_class_size <- filtered_data %>%
  group_by(sector) %>%
  summarize(average_size = mean(class_size))

# Plot the average class size by sector
ggplot(average_class_size, aes(x = sector, y = average_size)) +
  geom_bar(stat = "identity", fill = "blue") +
  labs(x = "Sector", y = "Average Class Size", title = "Average Class Size by Sector") +
  theme_bw()
```

```{r}

# Group the data by pentile and calculate the mean of hatamot_ivchun
hatamot_ivchun_by_pentile <- merged_data %>%
  group_by(pentile) %>%
  summarize(mean_hatamot_ivchun = mean(hatamot_ivchun, na.rm = TRUE))

# Print the result
print(hatamot_ivchun_by_pentile)
```

```{r}
# Calculate the sum of hatamot_ivchun and hatamot_no_ivchun
merged_data$hatamot_sum <- merged_data$hatamot_ivchun + merged_data$hatamot_no_ivhun

# Divide hatamot_sum into 5 bins
merged_data$ivchun_bins <- cut(merged_data$hatamot_sum, breaks = 10)

# Calculate the average math score for each bin
average_math_score <- merged_data %>%
  group_by(ivchun_bins) %>%
  summarize(average_math_score = mean(math_5_reg_ed, na.rm = TRUE))

# Create the bar plot
ggplot(average_math_score, aes(x = ivchun_bins, y = average_math_score)) +
  geom_bar(stat = "identity", fill = "blue") +
  labs(x = "Hatamot Total", y = "Average Math Score") +
  theme_minimal()
```
```{r}
## Relationship between math_5 and Pentiles with percentages of Hatamot Ivchun

# Filter the data for the year 2021
filtered_data <- merged_data %>%
  filter(year >= 2020)

# Create a new dataframe with the average hatamot_ivchun rate and math score by pentile
average_data <- filtered_data %>%
  group_by(pentile) %>%
  summarize(average_hatamot_ivchun = mean(hatamot_ivchun, na.rm = TRUE),
            average_math_score = mean(math_5_reg_ed, na.rm = TRUE))

# Create the bar plot
ggplot(average_data, aes(x = pentile, y = average_math_score, fill = average_hatamot_ivchun)) +
  geom_col() +
  labs(x = "Pentile", y = "Average Math Score", fill = "Average Hatamot Ivchun") +
  scale_fill_gradient(low = "light green", high = "dark green") +
  theme_minimal()
```

```{r}
# Divide hatamot_ivchun into 5 bins
merged_data$ivchun_bins <- cut(merged_data$hatamot_ivchun, breaks = 10)

# Calculate the average math score for each bin
average_math_score <- merged_data %>%
  group_by(ivchun_bins) %>%
  summarize(average_math_score = mean(math_5_reg_ed, na.rm = TRUE))

# Create the bar plot
ggplot(average_math_score, aes(x = ivchun_bins, y = average_math_score)) +
  geom_bar(stat = "identity", fill = "blue") +
  labs(x = "Hatamot Ivchun Bins", y = "Average Math Score") +
  theme_minimal()
```

```{r}
# Load the required packages
library(readxl)
library(dplyr)
library(stats)

# Read the Excel file
dataset1 <- read_excel("C:/Users/user/OneDrive/שולחן העבודה/Nevo/סמסטר ד/תכנות מתקדם לניתוח נתונים/פרוייקט גמר תכנות מתקדם/data/schools-aklim.xlsx")
dataset2 <- read_excel("C:/Users/user/OneDrive/שולחן העבודה/Nevo/סמסטר ד/תכנות מתקדם לניתוח נתונים/פרוייקט גמר תכנות מתקדם/data/schools-bagrut.xlsx")

# Perform the join operation
merged_data <- inner_join(dataset1, dataset2, by = c("school_id", "year"))

# Remove duplicate columns and keep only one column with the original name
merged_data <- merged_data %>%
  select(-ends_with(".y")) %>%
  rename_with(~ gsub("\\.x$", "", .), ends_with(".x"))

# Print the merged dataset with cleaned column names
print(merged_data)

# Select the relevant features and target
features <- features <- c('district', 'teacher_student_relations', 'reception_and_accompaniment', 'teacher_development', 'teaching_methods', 'self_teach_strategies', 'parents_involvement', 'positive_feeling')
target <- 'math_5_reg_ed'

# Filter the data and handle missing values if needed
filtered_data <- na.omit(merged_data[, c(features, target)])

# Prepare the feature matrix
X <- filtered_data[, setdiff(features, target)]

# Split the dataset into features and target variables
y <- filtered_data[[target]]

# Fit the linear regression model
regression_model <- lm(y ~ ., data = X)

# Print the coefficients (weights) and intercept
print("Intercept:")
print(regression_model$coefficients[1])
print("Coefficients:")
print(regression_model$coefficients[-1])
```


