---
title: "Project proposal"
author: "Team number 5"
mainfont: Roboto
output:
  github_document:
    toc: true
fig_caption: true
---
# Environment Setup

## Load Libraries
```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(htmltools)
library(readxl)
library(skimr)
library(stats)
library(cowplot)
```

## Read Tables
```{r get_file_names}
folder_path <- "../data"

# Get the list of files in the folder
file_list <- list.files(path = folder_path, pattern = "\\.xlsx$", full.names = TRUE)
```

### Read High-School Budget Table
```{r make_high_schools_budget, warning=FALSE}
high_schools_budget <- read_excel(file_list[1])

names(high_schools_budget) <- c(
    "hebrew_year", "del1", "muni_name", "sid", "school_name", "del13",
    "sector", "pentile", "pentile_type", "del2", "is_new_horizon",
    "teaching_hours", "teaching_cost", "tutor_hours", "del3", "del4", "del5",
    "del6", "tuition", "del7", "del8", "del9", "del10", "students_regular",
    "students_special", "number_of_classes", "number_of_special_classes",
    "del11", "del12", "total_budget"
)

high_schools_budget <- high_schools_budget[, -grep("^del[0-9]+$", names(high_schools_budget))]

high_schools_budget <- high_schools_budget %>%
  mutate(
    year = case_when(
      hebrew_year == "תשפא" ~ 2021,
      hebrew_year == "תשף" ~ 2020,
      hebrew_year == "תשעט" ~ 2019,
      hebrew_year == "תשעח" ~ 2018,
      hebrew_year == "תשעז" ~ 2017,
      hebrew_year == "תשעו" ~ 2016,
      hebrew_year == "תשעה" ~ 2015,
      hebrew_year == "תשעד" ~ 2014,
      TRUE ~ NA_integer_
      ),
    pentile = as.integer(as.character(pentile)),
    pentile_type = case_when(
      pentile_type == "לא מחושב" ~ NA_character_,
      TRUE ~ pentile_type
    ),
    is_new_horizon = case_when(
      is_new_horizon == 1 ~ TRUE,
      TRUE ~ FALSE
    )
  )
```

### Read Lamas Budget Table
```{r make_lamas_budget, warning=FALSE}
lamas_budget <- read_excel(file_list[2])

names(lamas_budget) <- c(
  "hebrew_year", "socio_economic_status", "del1", "del2", "del3",
  "teaching_hours", "teaching_cost", "tutor_hours", "staying_hours",
  "guidance_hours", "guidance_cost", "del4", "del5", "del6", "del7", "tuition",
  "del8", "perimeter_services_cost", "transportation_cost", "projects_cost",
  "purchases_cost", "del9", "maayan_hinuh_cost", "del10", "ptor_cost",
  "extras_ptor_cost", "number_of_students", "number_of_classes", "del11",
  "del12", "total_budget"
)

lamas_budget <- lamas_budget[, -grep("^del[0-9]+$", names(lamas_budget))]

lamas_budget <- lamas_budget %>%
  mutate(
    year = case_when(
      hebrew_year == "תשפא" ~ 2021,
      hebrew_year == "תשף" ~ 2020,
      hebrew_year == "תשעט" ~ 2019,
      hebrew_year == "תשעח" ~ 2018,
      hebrew_year == "תשעז" ~ 2017,
      hebrew_year == "תשעו" ~ 2016,
      hebrew_year == "תשעה" ~ 2015,
      hebrew_year == "תשעד" ~ 2014,
      TRUE ~ NA_integer_
      ),
    socio_economic_status = as.integer(as.character(socio_economic_status))
    )
```

### Read Municipal Table
```{r make_municipal_aklim, warning=FALSE}
municipal_aklim <- read_excel(file_list[3])

names(municipal_aklim) <- c(
  "mid", "muni_name", "del_edu_level", "hebrew_year", "respondents_teacher",
  "respondents_students", "respondents_teacher_percentage",
  "respondents_students_percentage", "del1", "del2", "del3", "del4", 
  "teacher_student_relations", "del5", "teacher_satisfaction", "del6", "del7",
  "del8", "reception_and_accompaniment", "del9", "violence", "del10",
  "interest", "del11", "teacher_development", "del12", "teaching_methods",
  "del13", "self_teach_strategies", "del14", "del15", "del16",
  "positive_feeling", "del17", "parents_involvement", "del18"
)

municipal_aklim <- municipal_aklim[, -grep("^del[0-9]+$", names(municipal_aklim))]

municipal_aklim <- municipal_aklim %>%
  filter(del_edu_level == 'חט"ע') %>%
  select(-del_edu_level) %>%
  mutate(
    year = case_when(
      hebrew_year == "תשפא" ~ 2021,
      hebrew_year == "תשף" ~ 2020,
      hebrew_year == "תשעט" ~ 2019,
      hebrew_year == "תשעח" ~ 2018,
      hebrew_year == "תשעז" ~ 2017,
      hebrew_year == "תשעו" ~ 2016,
      hebrew_year == "תשעה" ~ 2015,
      hebrew_year == "תשעד" ~ 2014,
      TRUE ~ NA_integer_
      )
  ) %>%
  mutate_all(~ ifelse(. == "-", NA, .))
```

### Read Municipal Budget Table
```{r make_municipal_budget, warning=FALSE}
municipal_budget <- read_excel(file_list[4])

names(municipal_budget) <- c(
  "hebrew_year", "mid", "district", "muni_name", "socio_economic_status",
  "del1", "del2", "del3", "teaching_hours", "teching_hours_cost", "tutor_hours",
  "staying_hours", "guidance_hours", "guidance_hours_cost", "del4", "del5",
  "del6", "del7", "tuition", "del8", "perimeter_services_cost",
  "transportation_cost", "projects_cost", "purchases_cost", "del9", 
  "maayan_hinuh_cost", "del10", "ptor_cost", "extras_ptor_cost", 
  "number_of_students", "del11", "number_of_classes", "del12","del13", "del13", 
  "del15", "total_budget"
)

municipal_budget <- municipal_budget[, -grep("^del[0-9]+$", names(municipal_budget))]

municipal_budget <- municipal_budget %>%
  mutate(
    year = case_when(
      hebrew_year == "תשפא" ~ 2021,
      hebrew_year == "תשף" ~ 2020,
      hebrew_year == "תשעט" ~ 2019,
      hebrew_year == "תשעח" ~ 2018,
      hebrew_year == "תשעז" ~ 2017,
      hebrew_year == "תשעו" ~ 2016,
      hebrew_year == "תשעה" ~ 2015,
      hebrew_year == "תשעד" ~ 2014,
      TRUE ~ NA_integer_
      )
  ) %>%
  mutate_all(~ ifelse(. == "-", NA, .)) %>%
  mutate(
    across(teaching_hours:total_budget, ~ as.numeric(.x))
  )

```

### Read Municipal Education Image Table
```{r make_municipal_edu_image, warning=FALSE}
municipal_edu_image <- read_excel(file_list[5])

names(municipal_edu_image) <- c(
  "hebrew_year", "muni_name", "mid", "socio_economic_status", "district", "del1", 
  "del2", "del3", "del4", "del5", "del6", "high_schools_students", "del7",
  "del8", "del9", "del10", "masters_or_higher_in_high_school", "hatamot_ivchun",
  "hatamot_no_ivchun", "olim", "spcecial_ed_in_reg", "del11", "del12",
  "number_of_classes", "del13", "del14", "del15", "total_teachers", "del16",
  "dropouts", "del17", "del18", "del19", "del20", "bagrut_entitlement",
  "bagrut_reg_ed", "bagrut_excel", "bagrut_reg_ed_excel", "english_4", 
  "english_4_reg_ed", "english_5", "english_5_reg_ed", "math_4", 
  "math_4_reg_ed", "math_5", "math_5_reg_ed", "del21", "del22", "del23",
  "del24", "del25", "del26", "class_size"
  )

municipal_edu_image <- municipal_edu_image[, -grep("^del[0-9]+$", names(municipal_edu_image))]

municipal_edu_image <- municipal_edu_image %>%
  mutate(
    year = case_when(
      hebrew_year == "תשפא" ~ 2021,
      hebrew_year == "תשף" ~ 2020,
      hebrew_year == "תשעט" ~ 2019,
      hebrew_year == "תשעח" ~ 2018,
      hebrew_year == "תשעז" ~ 2017,
      hebrew_year == "תשעו" ~ 2016,
      hebrew_year == "תשעה" ~ 2015,
      hebrew_year == "תשעד" ~ 2014,
      TRUE ~ NA_integer_
      ),
    socio_economic_status = as.integer(as.character(socio_economic_status))
  ) %>%
  mutate_all(~ ifelse(. == "לא רלוונטי", NA, .)) %>%
  mutate_all(~ ifelse(. == "לא מחושב", NA, .))
```

### Read School Aklim Table
```{r make_schools_aklim, warning=FALSE}
schools_aklim <- read_excel(file_list[6])

names(schools_aklim) <- c(
  "questionaire_year", "district", "sid", "school_name", "del1",
  "del_edu_level", "muni_name", "sector", "type", "respondents_teacher",
  "respondents_students", "respondents_teacher_percentage", 
  "respondents_students_percentage", "del2", "del3", "del4", "del5",
  "teacher_student_relations", "del6", "teacher_satisfaction", "del7", "del8",
  "del9", "reception_and_accompaniment", "del10", "violence", "del11",
  "interest", "del12", "teacher_development", "del13", "teaching_methods",
  "del14", "self_teach_strategies", "del15", "del16", "del17",
  "positive_feeling", "del18", "parents_involvement", "del19", "del20", "del21"
  )

schools_aklim <- schools_aklim[, -grep("^del[0-9]+$", names(schools_aklim))]

schools_aklim <- schools_aklim %>%
  select(-del_edu_level) %>%
  mutate_all(~ ifelse(. == "-", NA, .))
```

### Read School Education Image Table
```{r make_schools_edu_image, warning=FALSE}
schools_edu_image <- read_excel(file_list[8])
names(schools_edu_image) <- c(
  "hebrew_year", "educational_district", "sid", "mid", "muni_name", 
  "school_name", "exam_purity", "del1", "del2", "pentile_middle",
  "pentile_high", "del3", "decile_middle", "decile_high", "sector", "type",
  "from_grade", "to_grade", "school_plan", "tech", "del4", "olim",
  "is_special_ed", "school_type", "number_of_classes",
  "number_of_classes_yod_yodbet", "del5", "del6", "del7", "number_of_students",
  "number_of_students_yod_yodbet", "number_of_students_yodbet",
  "median_seniority", "total_teachers", "masters_or_higher_in_high_school",
  "hatamot_no_ivchun", "del8", "hatamot_ivchun", "del9", "special_ed", "del10",
  "del11", "dropouts", "del12", "del13", "del14", "dropouts_high_school",
  "youth_at_risk", "bagrut_school", "del15", "hila_students"
  )
schools_edu_image <- schools_edu_image[, -grep("^del[0-9\\w]+$", names(schools_edu_image))]
schools_edu_image <- schools_edu_image %>%
  mutate(
    year = case_when(
      hebrew_year == "תשפא" ~ 2021,
      hebrew_year == "תשף" ~ 2020,
      hebrew_year == "תשעט" ~ 2019,
      hebrew_year == "תשעח" ~ 2018,
      hebrew_year == "תשעז" ~ 2017,
      hebrew_year == "תשעו" ~ 2016,
      hebrew_year == "תשעה" ~ 2015,
      hebrew_year == "תשעד" ~ 2014,
      TRUE ~ NA_integer_
      )
  ) %>%
  mutate_all(~ ifelse(. == "לא רלוונטי", NA, .)) %>%
  mutate_all(~ ifelse(. == "לא מחושב", NA, .)) %>%
  mutate(
    tech = as.numeric(tech),
    olim = as.numeric(olim),
    across(number_of_classes:dropouts_high_school, ~ as.numeric(.x)),
    hila_students = as.numeric(hila_students)
  )
```

### Read School Bagrut Table
```{r make_schools_bagrut, warning=FALSE}
schools_bagrut <- read_excel(file_list[7])

names(schools_bagrut) <- c(
  "hebrew_year", "district", "muni_id", "muni_name", "sid", "school_name",
  "exam_purity", "pentile_youth", "sector", "type", "del1", "del2", "del3", "del4",
  "number_of_students_yodbet", "bagrut", "del5", "bagrut_reg_ed", "del6",
  "bagrut_excell", "del7", "bagrut_reg_ed_excell", "del8", "english_4", "del9",
  "english_4_reg_ed", "del10", "english_5", "del11", "english_5_reg_ed",
  "del12", "math_4", "del13", "math_4_reg_ed", "del14", "math_5", "del15",
  "math_5_reg_ed", "del16"
  )

schools_bagrut <- schools_bagrut[, -grep("^del[0-9]+$", names(schools_bagrut))]

schools_bagrut <- schools_bagrut %>%
  mutate(
    year = case_when(
      hebrew_year == "תשפא" ~ 2021,
      hebrew_year == "תשף" ~ 2020,
      hebrew_year == "תשעט" ~ 2019,
      hebrew_year == "תשעח" ~ 2018,
      hebrew_year == "תשעז" ~ 2017,
      hebrew_year == "תשעו" ~ 2016,
      hebrew_year == "תשעה" ~ 2015,
      hebrew_year == "תשעד" ~ 2014,
      TRUE ~ NA_integer_
      ),
    youth_at_risk = case_when(
      pentile_youth == "נוער בסיכון" ~ TRUE,
      TRUE ~ FALSE
    )
  ) %>%
  left_join(schools_edu_image[, c("year", "sid", "pentile_high")], by = c("year", "sid")) %>%
  mutate(pentile = pentile_high) %>%
  select(-pentile_youth, -pentile_high)
  
schools_bagrut <- schools_bagrut %>%
  mutate_all(~ ifelse(. == "לא רלוונטי", NA, .)) %>%
  mutate_all(~ ifelse(. == "לא מחושב", NA, .)) %>%
  mutate(across(number_of_students_yodbet:math_5_reg_ed, ~ as.numeric(.x)))

```

# Data Analyzing
## Linear Regression Model
```{r}
# Convert "mid" column to character type in municipal_aklim
municipal_aklim$mid <- as.character(municipal_aklim$mid)

# Perform the join operation
merged_data <- inner_join(schools_bagrut, schools_edu_image, by = c("sid", "year")) %>%
  inner_join(high_schools_budget, by = c("sid", "year")) %>%
  select(-ends_with(".y")) %>%
  select(-c("hebrew_year", "muni_name", "school_name", "sector")) %>%
  rename_with(~ gsub("\\.x$", "", .), ends_with(".x")) %>%
  mutate(
    class_size = number_of_students_yod_yodbet / number_of_classes_yod_yodbet,
    budget_per_student = total_budget / (students_regular + students_special)
  ) %>%
  inner_join(municipal_budget, by = c("mid", "year")) %>%
  inner_join(municipal_aklim, by = c("mid")) %>%
  mutate(
    teacher_student_relations = as.numeric(teacher_student_relations),
    parents_involvement = as.numeric(parents_involvement),
    violence = as.numeric(violence)
  )

# Print the merged dataset with cleaned column names
print(merged_data)

data <- merged_data
```

```{r}
# Select the relevant features and target
features <- c(
  'district.x',
  'pentile',
  'sector',
  'type',
  'school_type',
  'tech',
  'class_size',
  'bagrut',
  'masters_or_higher_in_high_school',
  'median_seniority',
  'bagrut_reg_ed',
  'hatamot_ivchun',
  'special_ed',
  'bagrut_excell',
  'bagrut_reg_ed_excell',
  'budget_per_student',
  'teaching_hours.y'
  )

target <- 'math_5_reg_ed'

# Filter the data and handle missing values if needed
filtered_data <- na.omit(data[, c(features, target)])

# Prepare the feature matrix
X <- filtered_data[, setdiff(features, target)]

# Split the dataset into features and target variables
y <- filtered_data[[target]]

# Split the data into training and test sets
set.seed(363)  # For reproducibility
train_indices <- sample(nrow(X), 0.7 * nrow(X))  # 80% for training
train_X <- X[train_indices, ]
train_y <- y[train_indices]
test_X <- X[-train_indices, ]
test_y <- y[-train_indices]

# Fit the linear regression model on the training data
regression_model <- lm(train_y ~ ., data = train_X)

# Print the coefficients (weights) and intercept
print("Intercept:")
print(regression_model$coefficients[1])
print("Coefficients:")
print(regression_model$coefficients[-1])

# Predict on the test set
predictions <- predict(regression_model, newdata = test_X)

# Calculate the adjusted R-squared
n <- length(test_y)
p <- length(regression_model$coefficients) - 1
adj_r_squared <- 1 - ((1 - summary(regression_model)$r.squared) * (n - 1) / (n - p - 1))
print("Adjusted R-squared:")
print(adj_r_squared)

# Calculate the mean squared error (MSE)
mse <- mean((predictions - test_y)^2)
print("Mean Squared Error (MSE):")
print(mse)

# Calculate the root mean squared error (RMSE)
rmse <- sqrt(mse)
print("Root Mean Squared Error (RMSE):")
print(rmse)

# Diagnostic tests
# 1. Residuals vs. Fitted Values Plot
plot(regression_model$fitted.values, regression_model$residuals, xlab = "Fitted Values", ylab = "Residuals", main = "Residuals vs. Fitted Values Plot")

# 2. Normal Q-Q Plot of Residuals
{qqnorm(regression_model$residuals, main = "Normal Q-Q Plot of Residuals")
qqline(regression_model$residuals)}

# 3. Scale-Location Plot
sqrt_abs_residuals <- sqrt(abs(regression_model$residuals))
{plot(regression_model$fitted.values, sqrt_abs_residuals, xlab = "Fitted Values", ylab = "Square Root of Absolute Residuals", main = "Scale-Location Plot")
abline(h = mean(sqrt_abs_residuals), col = "red")}

```
## Plots
### 5 Points Math Entitlement by Pentile and District
```{r message=FALSE}
# Perform the join operation
# Remove duplicate columns and keep only one column with the original name
# Filter data for the years 2020-2021 Drop rows with NA values in pentile or math_5_reg_ed columns
average_scores <- inner_join(schools_bagrut, schools_edu_image, by = c("sid", "year")) %>%
  select(-ends_with(".y")) %>%
  rename_with(~ gsub("\\.x$", "", .), ends_with(".x")) %>%
  filter(year %in% c("2020", "2021"), complete.cases(pentile, math_5_reg_ed)) %>% 
  group_by(pentile, district) %>% # Calculate the average math_5_reg_ed score for each pentile and district
  summarize(average_score = mean(math_5_reg_ed)) %>%
  mutate(district = fct_relevel(district, "צפון", "חיפה", "ירושלים", "דרום", "מנח'י", "חינוך התישבותי", "מרכז", "תל אביב", "חרדי"))

# Plot the average math_5_reg_ed scores
ggplot(average_scores, aes(x = pentile, y = average_score, fill = district)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +
  geom_vline(aes(xintercept = as.numeric(pentile) + 0.5), color = "black", linetype = "dashed", size = 0.5) +
  labs(x = "Pentile (Nurturing Index)", y = "5 Points Math Entitlement (%)", fill = "District") +
  ggtitle("5 Points Math Entitlement by Pentile and District") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
```

### 5 Points In Math by Academic Leniencies
```{r}
# Perform the join operation
# Remove duplicate columns and keep only one column with the original name
# Filter out rows where hatamot_sum is NA
# Adjust the scales of hatamot_sum and math_5_red_ed to range from 0 to 100
hatamot <- inner_join(schools_bagrut, schools_edu_image, by = c("sid", "year")) %>%
  select(-ends_with(".y")) %>%
  rename_with(~ gsub("\\.x$", "", .), ends_with(".x")) %>%
  drop_na(hatamot_ivchun, hatamot_no_ivchun) %>%
  mutate(
    hatamot_sum = round((hatamot_ivchun + hatamot_no_ivchun) * 100),
    math_5_reg_ed = math_5_reg_ed / 1000
    )

# Create the bar graph
ggplot(hatamot, aes(
  x = cut(hatamot_sum,
          breaks = seq(0, 100, by = 10),
          include.lowest = TRUE,
          labels = c("0-10", "10-20", "20-30", "30-40", "40-50", "50-60", "60-70", "70-80", "80-90", "90-100")
          ),
  y = math_5_reg_ed
  )) +
  geom_bar(stat = "identity", fill = "#00BFC4") +
  labs(x = "Academic Leniencies (With and Without Assessment) (%)",
       y = "5 Points In Math (%)",
       title = "5 Points In Math by Academic Leniencies") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme_minimal()
```

### Leniencies
```{r message=FALSE, warning=FALSE, results='hide'}
# Step 1: Perform an inner join
joined_data <- inner_join(schools_bagrut, schools_edu_image, by = c("sid", "year"))

# Remove duplicate columns and keep only one column with the original name
joined_data <- joined_data %>%
  select(-ends_with(".y")) %>%
  rename_with(~ gsub("\\.x$", "", .), ends_with(".x"))

joined_data$hatamot_sum <- (joined_data$hatamot_ivchun + joined_data$hatamot_no_ivchun)

# Create subsets based on total hatamot threshold
subset1 <- filter(joined_data, hatamot_sum >= 0.7)
subset2 <- filter(joined_data, hatamot_sum < 0.7)

# Calculate proportions for youth_at_risk and pentile within each subset
prop_youth_at_risk_subset1 <- nrow(filter(subset1, youth_at_risk)) / nrow(subset1)
prop_youth_at_risk_subset2 <- nrow(filter(subset2, youth_at_risk)) / nrow(subset2)

# Plot 1: Proportion of youth_at_risk = TRUE
plot1 <- ggplot() +
  geom_bar(data = data.frame(x = c("Leniencies >= 70%", "Leniencies < 70%"),
                             prop = c(prop_youth_at_risk_subset1, prop_youth_at_risk_subset2)),
           aes(x, prop * 100, fill = x), stat = "identity") +
  scale_fill_manual(values = c("#F8766D", "#00BFC4"), guide = FALSE) +
  labs(x = "", y = "Youth at Risk (%)", title = "Proportion of Youth at Risk") +
  scale_y_continuous(limits = c(0, 30)) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_minimal()

# Plot 2: Average special_ed
plot2 <- ggplot() +
  geom_bar(data = subset1, aes(x = "Leniencies >= 70%", y = special_ed * 100), stat = "summary", fill = "#00BFC4") +
  geom_bar(data = subset2, aes(x = "Leniencies < 70%", y = special_ed * 100), stat = "summary", fill = "#F8766D") +
  labs(x = "", y = "Special Education (%)", title = "Average Special Education") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_minimal()

cowplot::plot_grid(plot1, plot2, nrow = 1)
```
### 5 Points In Math by Academic Leniencies (Among Jewish Education, 2nd Pentile)
```{r message=FALSE, warning=FALSE}
# Perform the join operation
merged_data <- inner_join(schools_bagrut, schools_edu_image, by = c("sid", "year")) %>%
  inner_join(high_schools_budget, by = c("sid", "year")) %>%
  select(-ends_with(".y")) %>%
  select(-c("hebrew_year", "muni_name", "school_name", "sector")) %>%
  rename_with(~ gsub("\\.x$", "", .), ends_with(".x")) %>%

view(merged_data)

# Perform the join operation
merged_data <- inner_join(schools_bagrut, schools_edu_image, by = c("sid", "year")) %>%
  select(-ends_with(".y")) %>%
  rename_with(~ gsub("\\.x$", "", .), ends_with(".x"))

# Filter the joined dataset based on the given criteria
filtered_high_schools <- merged_data %>%
  filter(pentile_high == "2", sector == "יהודי", year == 2021, type != "חרדי")

# Convert "hatamot_no_ivhun" and "hatamot_ivchun" columns to numeric
filtered_high_schools$hatamot_no_ivchun <- as.numeric(filtered_high_schools$hatamot_no_ivchun)
filtered_high_schools$hatamot_ivchun <- as.numeric(filtered_high_schools$hatamot_ivchun)

# Create a scatter plot
ggplot(filtered_high_schools, aes(x = (hatamot_no_ivchun + hatamot_ivchun)*100, y = math_5_reg_ed)) +
  geom_point() +
  labs(x = "Academic Leniencies (%)", y = "5 Points Math Entitlement (%)", title = "5 Points In Math by Academic Leniencies (Among Jewish Education, 2nd Pentile)") +
  theme(plot.title = element_text(hjust = 0.5))+
  theme_minimal()
```

### Distribution of Teachers with Master's Degree or Higher
```{r}
# Filter data from schools_edu_image for years 2020-2021 and remove rows with missing values
# Calculate the average masters_or_higher_in_high_school by pentile_high from schools_filtered
average_by_pentile <- schools_edu_image %>%
  filter(year >= 2018 & year <= 2021 & !is.na(pentile_high) & !is.na(masters_or_higher_in_high_school)) %>%
  group_by(pentile_high) %>%
  summarise(average_masters = mean(as.numeric(masters_or_higher_in_high_school)))

# Plot 1: Average masters_or_higher_in_high_school by pentile_high
plot1 <- ggplot(average_by_pentile, aes(pentile_high, average_masters)) +
  geom_bar(stat = "identity", fill = "#00BFC4") +
  labs(x = "Pentile (Nurturing Index)", y = "Masters or Higher (%)", title = "Average Masters or Higher by Pentile (2018-2021)") +
  theme_minimal() +
  theme(plot.title = element_text(size = 8, hjust = 0.5)) +
  scale_y_continuous(labels = function(x) x * 100)

# Filter data from municipal_edu_image for years 2020-2021 and remove rows with missing values
# Calculate the average masters_or_higher_in_high_school by socio_economic_status
average_by_socio_economic <- municipal_edu_image %>%
  filter(year >= 2018 & year <= 2021 & !is.na(socio_economic_status) & !is.na(masters_or_higher_in_high_school)) %>%
  mutate(
    masters_or_higher_in_high_school = as.numeric(masters_or_higher_in_high_school),
    socio_economic_status = factor(socio_economic_status, levels = c(9, 8, 7, 6, 5, 4, 3, 2, 1))
    ) %>%
  group_by(socio_economic_status) %>%
  summarise(average_masters = mean(masters_or_higher_in_high_school, na.rm = TRUE))

# Plot 2: Average masters_or_higher_in_high_school by socio_economic_status
plot2 <- ggplot(average_by_socio_economic, aes(socio_economic_status, average_masters)) +
  geom_bar(stat = "identity", fill = "#F8766D") +
  labs(x = "Socioeconomic Status", y = "Masters or Higher (%)", title = "Average Masters or Higher by Socio-economic Status (2018-2021)") +
  theme_minimal() +
  theme(plot.title = element_text(size = 8, hjust = 0.5)) +
  scale_y_continuous(labels = function(x) x * 100)

# Combine the plots into a single graph
combined_plot <- cowplot::plot_grid(plot1, plot2, nrow = 1)

# Display the combined graph
print(combined_plot)

```
